Non-word repetition in Yélî Dnye

### 2020-05-15 manuscript.Rmd
fixed yaml

---
title: "Non-word repetition in Yélî Dnye"
shorttitle        : "NWR in Yélî Dnye'"

author: 
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29, rue d'Ulm, 75005, Paris, France"
    email         : "alecristia@gmail.com"
  - name          : "Marisa Casillas"
    affiliation   : "2"
    address       : "Wundtlaan 1, 6525 XD, Nijmegen, The Netherlands"
    email         : "marisa.casillas@mpi.nl"

affiliation:
  - id            : "1"
    institution   : "LSCP, Département d’études cognitives, ENS, EHESS, CNRS, Université PSL"
  - id            : "2"
    institution   : "Max Planck Institute for Psycholinguistics"

author_note: >

@@

keywords          : "phonology, non-word repetition, development"
wordcount         : "xxx"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf

---

@@

- fix yaml
- add ana based on phonemes & expand on levenshtein
- add ana based on number of characters
- add summary of types of error: %semantic, %deletion (which sounds?) %subst (which are the most common sounds) 
- maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed)
- add analysis on the basis of demo chars
- discussion

>>>>

---
title             : "Non-word repetition in Yélî Dnye"
shorttitle        : "NWR in Yélî Dnye"

author: 
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29, rue d’Ulm, 75005 Paris, France"
    email         : "alecristia@gmail.com"
  - name          : "Marisa Casillas"
    affiliation   : "2"
    address       : "Wundtlaan 1, 6525 XD, Nijmegen, The Netherlands"
    email         : "marisa.casillas@mpi.nl"

affiliation:
  - id            : "1"
    institution   : "Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d'Etudes cognitives, ENS, EHESS, CNRS, PSL University"
  - id            : "2"
    institution   : "Max Planck Institute for Psycholinguistics"

authornote: |
  All data are made available in a repository in the Open Science Framework. AC acknowledges the support of the Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004, ANR-14-CE30-0003, ANR-17-EURE-0017); and the J. S. McDonnell Foundation Understanding Human Cognition Scholar Award.

@@

keywords          : "phonology, non-word repetition, development"
wordcount         : "~xxx words"

@@

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

@@

- add ana based on phonemes & expand on levenshtein
- add ana based on number of characters
- add summary of types of error: %semantic, %deletion (which sounds?) %subst (which are the most common sounds) 
- maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed)
- add analysis on the basis of demo chars
- discussion
